---
title: "p8105_Linear_Models"
author: "Felix Tran"
date: "November 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

# Airbnb example
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group,
         neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

### Fit a linear model of price on rating and borough
```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)
```

### Look at summary of the lm output
The lm output is very hard to work with. You can manipulate output using
summary() but it's annoying.
```{r}
summary(fit)
```

### Broom package makes life easier
glance() extracts the summary stats of lm(). tidy() extracts the coefficients,
test stats of lm() model. The tidied output is easier to manipulate for more 
analyses or for displaying results.
```{r}
fit %>% 
  broom::glance()

fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
```

### Can specify factor levels to set the reference group yourself
lm() transforms the boro variable into a factor using the first value
alphabetically (Bronx) as the reference group). fct_infreq() sets the factor 
levels with the most frequent value as the reference group.

Changing the reference group/re-leveling does not change the overall fit of the
model.
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(boro = fct_infreq(boro),
         room_type = fct_infreq(room_type))

fit = lm(price ~ stars + boro, data = nyc_airbnb)
fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
```

# Diagnostics
add_residuals() from the modelr package gives you the residuals from a tidied,
fitted model for every observation. The output is the the same dataset you put 
into it with an added column for the residuals.
```{r}
modelr::add_residuals(nyc_airbnb, fit)
```
You can plot the residuals or run tests on them to assess the fit of your model.

add_predictions() from modelr package is the same as add_residuals() except it
gives you the predicted y values based on the model for each observation.
```{r}
modelr::add_predictions(nyc_airbnb, fit)
```

