---
title: "Cross_validation"
author: "Felix Tran"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(mgcv)

set.seed(1)
```

# Create a nonlinear dataset as an example
```{r}
nonlin_df = tibble(
  id = 1:100,
  x = runif(100, 0, 1),
  y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
)

ggplot(nonlin_df, aes(x = x, y = y)) + geom_point() + theme_bw()
```

### Make a training and testing dataset
sample_n() takes random samples from our example dataset. anti_join() lets
take the remaining observations from the example dataset.
```{r}
train_df <- sample_n(nonlin_df, 80)
test_df <- anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

### Fitting some models
gam() fits a smooth curve through a given dataset.

Looking at the models, we can see the linear model is underfitting, the 
wiggly model is overfitting, and the middle model seems to be a good fit. 
```{r}
lin_mod = lm(y ~ x, data = train_df)
nonlin_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)

train_df %>% 
  add_predictions(nonlin_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  gather_predictions(lin_mod, nonlin_mod, wiggly_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_wrap(~model)
```

### Calculate RMSE to verify which model is the best fit
The nonlin_mod has the smallest RMSE, which suggests it is the best fit of the
3 models. We are calculating the RMSE on the test data (NOT the training data).
```{r}
rmse(lin_mod, test_df)

rmse(nonlin_mod, test_df)

rmse(wiggly_mod, test_df)
```

### Repeating the process to verify our previous result wasn't a fluke
Iterates random partitions. Gives you list cols of training and test datasets.
```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) 
```

```{r}
cv_df =
  cv_df %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(lin_mod    = map(train, ~lm(y ~ x, data = .x)),
         nonlin_mod = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
         wiggly_mod = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(rmse_lin    = map2_dbl(lin_mod, test, ~rmse(model = .x, data = .y)),
         rmse_nonlin = map2_dbl(nonlin_mod, test, ~rmse(model = .x, data = .y)),
         rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
Graphing the RMSE's of all the iterations, the linear model is the worst. 
The nonlinear model appears to have the best fit of the 3 models.

# Case study: Growth of Nepalese children
Question: Is arm circumference related to weight?
```{r}
child_growth = read_csv("./data/nepalese_children.csv")
```

```{r}
child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5)
```

### Fitting models
```{r}
child_growth =
  child_growth %>% 
  mutate(weight_sp = (weight > 7) * (weight - 7))

lin_mod = lm(armc ~ weight, data = child_growth)
pwl_mod = lm(armc ~ weight + weight_sp, data = child_growth)
nonlin_mod = gam(armc ~ s(weight), data = child_growth)

child_growth %>% 
  gather_predictions(lin_mod, pwl_mod, nonlin_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5) +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(~model)
```

### Making training and testing splits
```{r}
cv_df =
  crossv_mc(child_growth, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(lin_mod = map(train, ~lm(armc ~ weight, data = .x)),
         pwl_mod = map(train, ~lm(armc ~ weight + weight_sp, data = .x)),
         nonlin_mod = map(train, ~gam(armc ~ s(weight), data = as_tibble(.x)))) %>% 
  mutate(rmse_lin    = map2_dbl(lin_mod, test, ~rmse(model = .x, data = .y)),
         rmse_pwl = map2_dbl(pwl_mod, test, ~rmse(model = .x, data = .y)),
         rmse_nonlin = map2_dbl(nonlin_mod, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

